Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/experiment.tex
writing pass on experiment.tex

In this section we use chokepoint potential to examine three questions: 1) To
what extent does the current state of the AS-level Internet topology support
national governments' ability to censor and surveil Internet traffic and how does
this ability vary across nations? 2) How has this ability
evolved over time? and 3) How does our topological chokepoint measure correlate to
qualitative measures of Internet and press freedom?

Our experiments begin with the CAIDA AS relationship dataset for a particular timestamp.
These detail inferred relationships between ASes, with which we can use our simulation framework
to generate routing trees and then calculates the chokepoint potentials for each AS. We use these 
relationships to identify border ASes, and we use the Team Cymru ASN lookup service to map each AS to the 
country with which it is registered. \toolname{} returns both the set of routing trees built via simulation
and the chokepoint potential that was determined for each AS. The resulting data allows us to conduct
multiple levels of analysis. The resulting chokepoint potentials allow us to compare nations in regards
to what kind of border topology they have. We can answer whether many or few ASes are needed for a 
particular nation to intercept a majority of BGP paths, for instance. We can also compare the results
of experiments at different timestamps to monitor the evolution of a nation's national chokepoint potential,
indicating trends toward stronger chokepoints or, alteratively, more open borders.

% Chokepoints and Internet Freedom
If chokepoint potential can be leveraged to determine if a nation can
intercept many BGP paths with few ASes, it is possible that there is some correlation between
this ability and the Internet freedom of that nation. If a higher national chokepoint potential
for a nation is related to a less free Internet or press, this indicates that topology is linked
to censorship in some way, perhaps indicating that the flow of information through border ASes
is an important factor in interpreting a nations ability to censor their traffic. While a causal
direction cannot be inferred by such a relationship, it would strengthen the importance of chokepoint
potential as a measure of the evolutionary direction of the Internet.

We tested whether a significant relationship exists between our measure of
national chokepoints and two qualitative evaluations of communications Freedom. For
Internet Freedom we used the Freedom House's Freedom On The Net report
\cite{FOTN}. FOTN scores quantify the level of Internet freedom in countries.
Each country receives a numerical score from 0 (the most free) to 100 (the
least free). We compare our results to the FOTN scores by ranking nations
according to national breakthrough potential, particulary the number of border
ASes required to intercept 90\% of paths for each nation and viewing these
rankings against the FOTN scores. FOTN only includes 65 nations in the most recent
report (2017), so we also compare our measure with Freedom of the Press, which assessed
201 nations and territories.

>>>>

This section describes how we used \toolname{} to study three questions related to national borders and the BGP network:
(1) To
what extent do BGP networks today reflect national boundaries
%support
%national governments' ability to censor and surveil Internet traffic and
how do they vary across nations? (2) How has this structure evolved
over time? and (3) How do topological chokepoints correlate with
qualitative measures of Internet and press freedom?

All of our experiments used the relevant CAIDA AS relationship dataset for 
each timestamp we studied.  These contain inferred relationships
between ASes, which the simulation framework uses to
generate routing trees and  calculate chokepoint potentials.
We use the relationships to identify border ASes, and
we use the Team Cymru ASN lookup service to map each AS to the country
with which it is registered. \toolname{} returns both the set of
routing trees built via simulation and the chokepoint potential that
was determined for each AS. These data form the basis for
multiple levels of analysis: comparing chokepoint potential between countries,
assessing how many ASes are required to control most international BGP paths, 
and comparing results across multiple time points.
%timestamps to monitor the evolution of a nation's national chokepoint
%potential, indicating trends toward stronger chokepoints or,
%alteratively, more open borders.

% Chokepoints and Internet Freedom
Chokepoints provide one leverage point for nations interested in censorship or surveillance.
%potential can be leveraged to determine if a nation can
%intercept many BGP paths with few ASes, it is possible that there is some correlation between
Thus, we are interested in the extent to which the Internet freedom of a country correlates with its chokepoint potential.
%If a higher national chokepoint potential
%for a nation is related to a less free Internet or press, this indicates that topology is linked
%to censorship in some way, perhaps indicating that the flow of information through border ASes
%is an important factor in interpreting a nations ability to censor their traffic.
Although correlation certainly does not imply a causal relation, correlations can highlight overall trends and even provide clues about how censorship might be implemented in countries that are known to control content.
%direction cannot be inferred by such a relationship, it would strengthen the importance of chokepoint
%potential as a measure of the evolutionary direction of the Internet.
We tested the statistical relationship between national chokepoint potential
and two relevant qualitative evaluations of freedom. First, we used
Freedom House's Freedom On The Net report \cite{FOTN}. FOTN scores
quantify the level of Internet freedom in countries.  Each country
receives a numerical score from 0 (the most free) to 100 (the least
free). We compare our results to FOTN scores (for years 2014-2017) by ranking nations
according to the number of border ASes required to intercept 90\% of
paths for each nation.  FOTN includes only 65 nations in the most
recent report (2017), so we also compare to the Freedom of
the Press evaluation (2014-2017), which assesses 201 nations and territories.
